### 2012-04-18 docs/architecture/architecture.tex
fix the MAC velocity example

The MAC velocities are allocated at each level of refinement, {\tt n},
by making a \multifab\ array where each of the {\tt dm} components is
nodal in its respective direction:
\begin{lstlisting}[language={[95]fortran},mathescape=false]
  type(multifab) :: umac(dm)

  do comp=1,dm
     call multifab_build_edge(umac(n,comp), mla%la(n),1,1,comp)
  enddo
\end{lstlisting}

>>>>

The MAC velocities are allocated at each level of refinement, {\tt n},
by making a \multifab\ array where each of the {\tt dm} components is
nodal in its respective direction:
\begin{lstlisting}[language={[95]fortran},mathescape=false]
  type(multifab) :: umac(nlevel,dm)

  do n=1,nlevel
     do comp=1,dm
        call multifab_build_edge(umac(n,comp), mla%la(n),1,1,comp)
     enddo
  enddo
\end{lstlisting}
